\begin{thebibliography}{99} % two-digit numbers, max

\bibitem{afl}
  Michal Zalewski. % Author
  \textit{American Fuzzy Lop}. % Title
  \url{http://lcamtuf.coredump.cx/afl/}. % URL

\bibitem{vanhauser}
  Marc ``van Hauser'' Heuse.
  \textit{Collection of Patches to AFL}.
  \url{https://github.com/vanhauser-thc/afl-patches/}.

\bibitem{aflosx}
  Ben Nagy.
  \textit{AFL on OSX}.
  \url{https://github.com/bnagy/osx-afl-llvm}.

\bibitem{winafl}
  Ivan Fratric.
  \textit{WinAFL - Fork of AFL for Windows}.
  \url{https://github.com/ivanfratric/winafl}

\bibitem{netafl}
  Maksim Shudrak.
  \textit{winAFL patch to enable network-based apps fuzzing}.
  \url{https://github.com/mxmssh/netafl}

\bibitem{preeny}
  Yan Shoshitaishvili.
  \textit{Preeny: preload libraries for pwning stuff}.
  \url{https://github.com/zardus/preeny}

\bibitem{boinc}
  University of California.
  \textit{Berkeley Open Infrastructure for Network Computing}.
  \url{https://boinc.berkeley.edu/}.

\bibitem{peach22}
  Michael Eddington.
  \textit{Peach Fuzzer version 2.2}.
  \url{https://sourceforge.net/projects/peachfuzz/files/Peach/2.2/}.

\bibitem{aflfast}
  Marcel B\"ohme, Van-Thuan Pham, Abhik Roychoudhury.
  \textit{Coverage-based Greybox Fuzzing as Markov Chain}.
  \url{https://www.comp.nus.edu.sg/~mboehme/paper/CCS16.pdf}.

\bibitem{aflgo}
  Marcel B\"ohme, Van-Thuan Pham, Manh-Dung Nguyen, Abhik Roychoudhury.
  \textit{Directed Greybox Fuzzing}.
  \url{https://mboehme.github.io/paper/CCS17.pdf}.

\bibitem{fairfuzz}
  Caroline Lemieux, Koushik Sen.
  \textit{FairFuzz: Targeting Rare Branches to Rapidly Increase Greybox Fuzz Testing Coverage}.
  \url{https://arxiv.org/pdf/1709.07101.pdf}.

\bibitem{perffuzz}
  Caroline Lemieux, Rohan Padhye, Koushik Sen, Dawn Song.
  \textit{PerfFuzz: automatically generating pathological inputs}.
  \url{https://dl.acm.org/citation.cfm?doid=3213846.3213874}.

\bibitem{pythia}
  Marcel B\"ohme.
  \textit{STADS: Software Testing as Species Discovery}.
  \url{https://mboehme.github.io/paper/TOSEM18.pdf}.

\bibitem{collafl}
  Shuitao Gan, Chao Zhang, Xiaojun Qin, Xuwen Tu, Kang Li, Zhongyu Pei, Zuoning Chen.
  \textit{CollAFL: Path Sensitive Fuzzing}.
  \url{http://chao.100871.net/papers/oakland18.pdf}.

\bibitem{syzkaller}
  Google.
  \textit{syzkaller - kernel fuzzer}.
  \url{https://github.com/google/syzkaller}.

\bibitem{ossfuzz}
  Google.
  \textit{OSS-Fuzz - Continuous Fuzzing for Open Source Software}.
  \url{https://github.com/google/oss-fuzz}.

\bibitem{driller}
  Nick Stephens, John Grosen, Christopher Salls, Audrey Dutcher, Ruoyu Wang,
  Jacopo Corbetta, Yan Shoshitaishvili, Christopher Kruegel, Giovanni Vigna.
  \textit{Driller: Augmenting Fuzzing Through Selective Symbolic Execution}.
  \url{http://www.cs.ucsb.edu/~chris/research/doc/ndss16_driller.pdf}.

\bibitem{pin}
  Intel Corporation.
  \textit{Pin - A Dynamic Binary Instrumentation Tool}.
  \url{https://software.intel.com/en-us/articles/pin-a-dynamic-binary-instrumentation-tool}.

\bibitem{ni}
  Aki Helin.
  \textit{Ni mutator}.
  \url{https://github.com/aoh/ni}.

\bibitem{radamsa}
  Aki Helin.
  \textit{Radamsa - a general-purpose fuzzer}.
  \url{https://gitlab.com/akihe/radamsa}.

\bibitem{zzuf}
  Sam Hocevar.
  \textit{zzuf - general purpose fuzzer}.
  \url{https://github.com/samhocevar/zzuf}.

\bibitem{synfuzz}
  Joe Rozner.
  \textit{Synfuzz - re-targetable grammar based test case generation}.
  \url{https://github.com/jrozner/synfuzz}.

\bibitem{dyninst}
  The University of Wisconsin, University of Maryland.
  \textit{DyninstAPI: Tools for binary instrumentation, analysis, and modification}.
  \url{https://dyninst.org/}.

\bibitem{brundlefuzz}
  Carlos Garcia Prado.
  \textit{BrundleFuzz - a distributed fuzzer for Windows and Linux using dynamic binary instrumentation}.
  \url{https://github.com/carlosgprado/BrundleFuzz}.

\bibitem{angora}
  Peng Chen, Hao Chen.
  \textit{Angora: Efficient Fuzzing by Principled Search}.
  \url{https://angorafuzzer.github.io/}.

\bibitem{intelptmanual}
  Intel Corporation.
  \textit{Intel® 64 and IA-32 Architectures Software Developer's Manual Volume 3C: System Programming Guide, Part 3, p248}.
  \url{https://software.intel.com/en-us/download/intel-64-and-ia-32-architectures-sdm-volume-3c-system-programming-guide-part-3}.

\bibitem{libipt}
  Intel Corporation.
  \textit{libipt - an Intel(R) Processor Trace decoder library }.
  \url{https://github.com/01org/processor-trace}.

\bibitem{winaflintelpt}
  Ivan Fratric, Richard Johnson.
  \textit{Fork of WinAFL}.
  \url{https://github.com/intelpt/winafl-intelpt/}.

\bibitem{winaflcommit}
  Richard Johnson.
  \textit{Commit which appears to have removed IPT support}.
  \url{https://github.com/intelpt/winafl-intelpt/commit/d1e9e560bbaf4e56f6d6bd48672bf691097e86fa}.

\bibitem{qemuspeedup}
  Andrea Biondo.
  \textit{Improving AFL's QEMU mode performance}.
  \url{https://abiondo.me/2018/09/21/improving-afl-qemu-mode/}.

\bibitem{peach}
  Peach Tech.
  \textit{Peach Fuzzer}.
  \url{https://www.peach.tech/}.

\bibitem{honggfuzz}
  Google.
  \textit{Honggfuzz - A security oriented, feedback-driven, evolutionary, easy-to-use fuzzer with interesting analysis options}.
  \url{http://honggfuzz.com/}.

\bibitem{honggfuzzgrimm}
  GRIMM.
  \textit{Modified version of Honggfuzz which enables it to use Killerbeez mutator modules}.
  \url{https://github.com/grimm-co/honggfuzz}.

%\bibitem{}
%  .
%  \textit{}.
%  \url{}.

\end{thebibliography}
