\documentclass{article}
\title{Killerbeez API}
\author{GRIMM}
\date{2017.12.22}
\input{defines}

\begin{document}
% Nice cover page
\thispagestyle{empty}
\maketitle
\newpage

% Table of Contents
\tableofcontents
\newpage

\section{Overview}
This document will cover the specific API of each module, along with a quick
high-level summary of what it does.

\par
The APIs are all specified in C, as this provides a consistent language and is
explicit about data types which means there's no need for a separate Python
specification.  The C code is frequently wrapped with python (via ctypes), but
modules are often included as pure C code as they run considerably faster when
it is all native code.

\section{Manager}
The manager it what coordinates a fuzz job.  It decides which seeds to use,
which mutators to run and kicks off one or more Main Fuzzers.

\section{Main Fuzzer}
This will run many iterations of a single seed and a single mutator against a
target program.  For efficiency, this will be run on the same computer (which
means same O/S) as the target binary.  This component will be an executable that
the manager executes on each of the target systems.  The arguments for this
function are defined in the usage function of the fuzzer.

\section{Mutator}
\input{api_mutator}

%\section{Driver}
% TODO: document me!

%\section{Instrumentation}
% TODO: document me!

%\section{Database}
% TODO: document me!

%\section{Tracer}
% TODO: document me!

%\section{Input Generator}
% TODO: create me and then document me!

\end{document}

